---
name: Dionne
surname: Argyropoulos
position: "PhD"
pronouns: she/her
address: "Infecton and Global Health Division, Walter & Eliza Hall Institute"
phone: +61 411 394 914
email: "argyropoulos.d@wehi.edu.au"
github: dionnecargy
linkedin: dionneargy
orcid: "0000-0002-8068-0215"
googlescholar: "clSfd8kAAAAJ"
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "000000"
output:
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(scholar)
library(tibble)
library(tidyverse)
library(here)
library(kableExtra)
options(tinytex.verbose = TRUE)

readExcelSheets <- function(filename){
  # read all sheets in .xlsx 
  all <- readxl::excel_sheets(filename)
  
  # import each sheet into a list using readxl::read_excel
  list <- lapply(all, function(x) readxl::read_excel(filename, sheet = x))
  
  # save sheet name for each sheet (list)
  names(list) <- all
  
  # breaks up list and creates a dataframe for each sheet with df names matching sheet names
  list2env(list, envir = .GlobalEnv)
}

readExcelSheets(here::here("data", "CV_DA_2026.xlsx"))
```

# About Me

\footnotesize

I have an avid interest in genetics and evolution which led me to apply these approaches to studies of infectious diseases, such as *Plasmodium falciparum* malaria in my Masters of Science and PhD, to *P. vivax* malaria and various microbes in my current first post-doc position. I am also an active member of the R-Ladies+ Melbourne community and continue to contribute to Women in STEM based volunteering programs. Throughout my research projects, I have developed a deep interest in coding and have even generated this CV using R!

\normalsize

# Current Position

```{r positions}
d <- data.frame(
  what = "Research Officer",
  when = "2024-current",
  with = "Walter and Eliza Hall Institute of Medical Research (WEHI)",
  where = "Melbourne, AU",
  why = "Post-doctoral researcher with a focus on machine learning and advanced epidemiological methods."
)
d %>%
  detailed_entries(
    what = what,
    when = when,
    with = with,
    where = where,
    .protect = FALSE
  )
```

# Education

```{r education}
education %>% 
  detailed_entries(
    what = degree, 
    when = year, 
    with = institution, 
    where = where,
    .protect = FALSE
  ) %>% 
  group_by(what, when, with, where)
```

# Publications

Shown are selected publications with first, second or third-author contributions. 

```{r, echo=FALSE}
publications %>%
  filter(selected == "y") %>% 
  detailed_entries(
    what = paste(author, " ", doi),
    when = year,
    with = title,
    where = journal
  ) %>%
  arrange(desc(when))
```

# Teaching and Supervision

\footnotesize

I have been actively involved in the fostering collaboration with researcher officers from the Noguchi Memorial Institute for Medical Research in Ghana (2021-2023), University of Chicago, USA (2021-2023) Institut Pasteur Cambodia (2026) to develop and expand skills in R, population genetics, infectious disease modelling and/or epidemiology.

I have also had casual employment with the University of Melbourne to teach various subjects in Biology, Genetics and Evolution (2018-2021) and was a tutor employed my the Indigenous Tutorial Access Scheme (ITAS, 2019). I am currently working with WEHI to develop and give R-related workshops and courses. 

\normalsize

# Conference Presentations

Shown are select conferences where I have presented a poster and/or a talk. 

```{r conferences}
conferences %>%
  filter(role!="Attendee") %>% 
  filter(selected=="y") %>%
  brief_entries(
    what = glue::glue(
      "\\textbf{<conference>} (<role>): <details>", 
      .open = "<", 
      .close = ">"
    ),
    paste0(dates, "\\newline~\\newline"), 
    .protect = FALSE
  )
```

# Awards and Funding

```{r}
awards %>%
  filter(selected=="y") %>%
  mutate(
    institution = gsub("The University of Melbourne", "UoM", institution),
    details = gsub("\\(ESPIDAM)", "", details),
    details = gsub("the European Summer Program in Infectious Disease Analysis and Modelling", "ESPIDAM", details)
  ) %>% 
  brief_entries(
    glue::glue("\\textbf{<award>} (<institution>): <details>", .open = "<", .close = ">"),
    paste0(year, "\\newline~\\newline"), 
    .protect = FALSE
  )
```

# Leadership, Service & Community Engagement

```{r volunteering}
volunteering %>%
  filter(selected=="y") %>% 
  detailed_entries(
    what = where,
    when = dates, 
    with = institution,
    where = role,
    why = details,
    .protect = FALSE
  )
```
